\documentclass[aspectratio=169]{beamer}
\usetheme{Madrid}

% Title and Author Information
\title[AI in Education]{Artificial Intelligence in Education}
\subtitle{SCH 261: Engineering Project Management}
\author{
  Ahmad Yasser (202200477) \\
  SalahDin Rezk (202201079) \\
  Youssef Allam (202200286) \\
  Ziad Haitham (202201027)
}
\date{Supervised by Dr. Hassan Darwish}

% Begin Document
\begin{document}

% Title Slide
\begin{frame}
  \titlepage
\end{frame}

% Table of Contents
\begin{frame}{Table of Contents}
  \tableofcontents
\end{frame}

% Sections Begin
\section{Background and Business Opportunity}
\begin{frame}{Background and Business Opportunity}
  \begin{itemize}
    \item AI offers tremendous benefits in education but can also be misused.
    \item Goal: Create customized educational models ensuring proper understanding and guided learning.
  \end{itemize}
\end{frame}

\section{Objectives of the Project}
\begin{frame}{Objectives}
  \begin{itemize}
    \item Provide educational AI models for schools, universities, and self-learners.
    \item Optimize AI usage to enhance learning without compromising educational integrity.
    \item Personalize learning through the VARK learning styles.
  \end{itemize}
\end{frame}

\section{Project Constraints and Risks}
\begin{frame}{Constraints and Risks}
  \textbf{Constraints:}
  \begin{itemize}
    \item Initial focus on select educational institutions.
    \item Gradual expansion.
  \end{itemize}
  \textbf{Risks:}
  \begin{itemize}
    \item Resistance from educators and institutions.
    \item Student preference for standard models.
    \item Compatibility with diverse curricula and systems.
    \item Accuracy of the AI model.
  \end{itemize}
\end{frame}

\section{Communication Plan and Resources}
\begin{frame}{Communication Plan}
  \begin{itemize}
    \item Demonstrate model benefits to institution administrators.
    \item Provide demo sessions and emphasize accuracy.
  \end{itemize}
  \textbf{Resources:}
  \begin{itemize}
    \item Educational experts and developers.
    \item Marketing team with knowledge in AI and education.
    \item Servers and maintenance teams.
  \end{itemize}
\end{frame}

\section{Risk Management}
\begin{frame}{Risk Management Strategies}
  \begin{itemize}
    \item \textbf{Resistance from Educators:} Strong marketing strategies and demos.
    \item \textbf{Student Preferences:} Campus sessions and rewards programs.
    \item \textbf{Compatibility:} Involvement of experts from various systems.
    \item \textbf{Model Accuracy:} Continuous improvement and reference validation.
  \end{itemize}
\end{frame}

\section{Project Cost Management}
\begin{frame}{Cost Management}
  \textbf{Cost Estimation:}
  \begin{itemize}
    \item Total Budget: \$3,100,000 (~160M EGP).
    \item Major Activities: Development, launch, marketing, and salaries.
  \end{itemize}
  \textbf{Cost Control:}
  \begin{itemize}
    \item Biweekly budget reviews.
    \item Adjustments based on departmental spending.
  \end{itemize}
\end{frame}

\section{Activities}
\begin{frame}{Key Activities}
  \textbf{Planning:}
  \begin{itemize}
    \item Surveys with students, instructors, and experts.
    \item Research on AI tools and market gaps.
  \end{itemize}
  \textbf{Development:}
  \begin{itemize}
    \item Prototype creation and iterative testing.
    \item Feedback channels for refinement.
  \end{itemize}
\end{frame}

\section{KPIs}
\begin{frame}{Key Performance Indicators (KPIs)}
  \begin{itemize}
    \item \textbf{Prototype Testing:} Over 200 test usages per system.
    \item \textbf{Model Usage:} 50\% of students in partner institutions.
    \item \textbf{Engagement:} 4 hours of weekly usage per student.
    \item \textbf{Student Performance:} 20\% improvement in scores.
    \item \textbf{Satisfaction:} Net Promoter Score of 7+.
  \end{itemize}
\end{frame}

% Closing Slide
\begin{frame}{Thank You!}
  \centering
  Questions or Feedback?
\end{frame}

\end{document}
